junk_final_assignment

### 2022-11-27 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

##Creatung a dfm from the corpus
```{r}
dfm <- corp %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

@@

dfm %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```

#Wordcloud comparing Democrats and Republicans
```{r}
dfmat2 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmat2, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

@@

#Wordcloud comparing Congress
```{r}
dfmat3 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmat3, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

>>>>

##Creatung a dfm from the corpus
```{r}
dfm_corp <- corp %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

@@

dfm_corp %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```

#Wordcloud congress 116

```{r}
dfmat116 <- dfm(corpus_subset(corp, Congress == 116), remove = stopwords("english"), remove_punct = TRUE) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat116, max_words = 300)

@@

#Wordcloud congress 117

```{r}
dfmat117 <- dfm(corpus_subset(corp, Congress == 117), remove = stopwords("english"), remove_punct = TRUE) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat117, max_words = 300)

#Wordcloud comparing Democrats and Republicans
```{r}
dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

#Wordcloud comparing Congresses
```{r}
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))
